Manuscript progress report

### 2024-09-02 Docs/manuscript.Rmd
rerun small simulation

---
title: "Manuscript progress report"
author: "Ying Jin"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: no
    number_sections: yes
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float: yes
    font: 12pt
    keep_tex: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
    keep_tex: yes
---

>>>>

---
title: "Manuscript progress report"
author: "Ying Jin"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: yes
    number_sections: yes
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float: yes
    font: 12pt
    keep_tex: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
    keep_tex: yes
---
